Draft

### 2020-04-22 SubGroup.Rmd
update

Referral_long  <- subset(MDF_long, MDF_long$UseCase %in% "PrivatePublicReferral")
DOTS_long  <- subset(MDF_long, MDF_long$UseCase %in% "PublicDOTSRetesting")
WalkIn_long  <- subset(MDF_long, MDF_long$UseCase %in% "WalkIn")
# 
# 
# New_Yong <- MDF[MDF$TB.Medication.History %in% "No" & MDF$AgeGroup %in% "[15,25)",]
# Old_Yong <- MDF[MDF$TB.Medication.History %in% "Yes"& MDF$AgeGroup %in% "[15,25)",]
# 
# New_Middle <- MDF[MDF$TB.Medication.History %in% "No" & MDF$AgeGroup %in% "[25,60)",]
# Old_Middle <- MDF[MDF$TB.Medication.History %in% "Yes"& MDF$AgeGroup %in% "[25,60)",]
# 
# New_Senior <- MDF[MDF$TB.Medication.History %in% "No" & MDF$AgeGroup %in% "[60,108]",]
# Old_Senior <- MDF[MDF$TB.Medication.History %in% "Yes"& MDF$AgeGroup %in% "[60,108]",]

# Missing_long  <- subset(MDF, is.na(MDF$UseCase)==T)

# source("Chapter/Subgroup Table/Young.R")
# source("Chapter/Subgroup Table/Middle.R")
# source("Chapter/Subgroup Table/Senior.R")
# source("Chapter/Subgroup Table/Referral.R")
# source("Chapter/Subgroup Table/DOTS.R")
# write.csv(CAD_Xpert_plot_Middle, "Chapter/Subgroup Table/CAD_Xpert_plot_Middle.csv")
# write.csv(CAD_Xpert_plot_Young, "Chapter/Subgroup Table/CAD_Xpert_plot_Young.csv")
# write.csv(CAD_Xpert_plot_Senior, "Chapter/Subgroup Table/CAD_Xpert_plot_Senior.csv")
# write.csv(CAD_Xpert_plot_Referral, "Chapter/Subgroup Table/CAD_Xpert_plot_Referral.csv")
# write.csv(CAD_Xpert_plot_DOTS, "Chapter/Subgroup Table/CAD_Xpert_plot_DOTS.csv")
# write.csv(CAD_Xpert_plot_WalkIn, "Chapter/Subgroup Table/CAD_Xpert_plot_WalkIn.csv")
# write.csv(CAD_Xpert_plot_New, "Chapter/Subgroup Table/CAD_Xpert_plot_New.csv")
# write.csv(CAD_Xpert_plot_Old, "Chapter/Subgroup Table/CAD_Xpert_plot_Old.csv")

# CAD_Xpert_plot_Middle <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Middle.csv")
# CAD_Xpert_plot_Young <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Young.csv")
# CAD_Xpert_plot_Senior <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Senior.csv")
# CAD_Xpert_plot_DOTS <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_DOTS.csv")
# CAD_Xpert_plot_WalkIn <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_WalkIn.csv")
# CAD_Xpert_plot_Referral <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Referral.csv")
# CAD_Xpert_plot_New <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_New.csv")
# CAD_Xpert_plot_Old <- read.csv("Chapter/Subgroup Table/CAD_Xpert_plot_Old.csv")
# 
# 
# SubgroupTable <- rbind(CAD_Xpert_plot_New, CAD_Xpert_plot_Old, CAD_Xpert_plot_Young, CAD_Xpert_plot_Middle, CAD_Xpert_plot_Senior, CAD_Xpert_plot_Referral, CAD_Xpert_plot_DOTS, CAD_Xpert_plot_WalkIn)
# write.csv(SubgroupTable, "Chapter/Subgroup Table/SubgroupTable.csv", row.names = F)
# rm(list=(ls()))
```

@@

# l <- ROCPRC(New_Yong)
# New_Yong <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
# New_Yong$subgroup <- "New_Yong"
# 
# 
# l <- ROCPRC(New_Middle)
# New_Middle <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
# New_Middle$subgroup <- "New_Middle"
# 
# 
# l <- ROCPRC(New_Senior)
# New_Senior <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
# New_Senior$subgroup <- "New_Senior"
# 
# 
# 
# l <- ROCPRC(Old_Yong)
# Old_Yong <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
# Old_Yong$subgroup <- "Old_Yong"
# 
# 
# l <- ROCPRC(Old_Middle)
# Old_Middle <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
# Old_Middle$subgroup <- "Old_Middle"
# 
# 
# 
# l <- ROCPRC(Old_Senior)
# Old_Senior <- data.frame(matrix(unlist(l), nrow=5, byrow=T))
# Old_Senior$subgroup <- "Old_Senior"
# 
# 
# temp <- rbind(New_Yong, New_Middle, New_Senior, Old_Yong, Old_Middle, Old_Senior)
# colnames(temp) <- c("DL.System", "AUC", "PCAUC", "Subgroup")
# temp$AUC <- as.numeric.factor(temp$AUC)
# temp$PCAUC <- as.numeric.factor(temp$PCAUC)

# View(temp)

# ggplot(temp, aes(x=DL.System, y=AUC, fill=Subgroup))+  geom_bar(stat="identity", width=0.6, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

aucTable <- rbind(all, New, Old, Young, Middle, Senior, Referral, DOTS, WalkIn, Female, Male)
colnames(aucTable) <- c("DL System", "AUC", "PCAUC", "Subgroup")
write.csv(aucTable, "Results/aucTable.csv")
# rm(list=(ls()))
```

@@

### AUC
age<-ggplot(aucTable[aucTable$Subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=DL.System, y=AUC, fill=Subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))

>>>>

Referral_long  <- subset(MDF_long, MDF_long$UseCase %in% "PrivatePublicReferral")
DOTS_long  <- subset(MDF_long, MDF_long$UseCase %in% "PublicDOTSRetesting")
WalkIn_long  <- subset(MDF_long, MDF_long$UseCase %in% "WalkIn")

@@

aucTable <- rbind(all, New, Old, Young, Middle, Senior, Referral, DOTS, WalkIn, Female, Male)
colnames(aucTable) <- c("DL System", "AUC", "PCAUC", "Subgroup")
# write.csv(aucTable, "Results/aucTable.csv")
# rm(list=(ls()))
```

@@

aucTable$Subgroup <- factor(aucTable$Subgroup, levels = c("Young age", "Middle age", "Old age", "Referred", "DOTS retested", "WalkIn", "New cases", "Previously treated cases", "Female", "Male"))
### AUC
age<-ggplot(aucTable[aucTable$Subgroup %in% c("Young age", "Middle age", "Old age"), ], aes(x=DL.System, y=AUC, fill=Subgroup)) +  geom_bar(stat="identity", width=0.6, position=position_dodge())+theme_minimal()+ theme(legend.position = "top")+  ylim(0, 0.95) + theme(panel.grid.minor = element_line(size=0.5)) + scale_y_continuous(minor_breaks = seq(0 , 0.95, 0.05), breaks = seq(0.65, 0.95, 0.05))
